\section*{2/25}
  From last time,\\
  \underline{Example}:
    $$
      f(x,y) = \begin{cases} \frac{21}{4}x^2y & x^2 \le y < 1\\ 0 & \text{
      otherwise} \end{cases}
    $$
    Compute marginal densities. Independence?\\
    $$
      f_X(x) = \int_{x^2}^1 \frac{21}{4} x^2y \, dy = \frac{21}{8} x^2(1-x^4)
    $$
    where $x \in (-1, 1]$.\\
    \underline{Note}: The range is from $x^2$ to 1 because we are measuring
    the area from $y = x^2$ to $y = 1$.\\\\
    $$
      f_Y(y) = \int_{-\sqrt{y}}^{\sqrt{y}} \frac{21}{4}x^2y\,dx = \frac{7}{2}
      y^{\frac{5}{2}}
    $$
    where $y \in [0,1]$\\
    \underline{Note}: The range is from $-\sqrt{y}$ to $\sqrt{y}$ because we 
    are measuring the area from the curve $x = -\sqrt{y}$ and $x = \sqrt{y}$.\\
    They are not independent because if you multiply the two marginal densities,
    you don't get the $f(x,y)$.\\\\
  \underline{Example}: $(X, Y)$ are random points in the square of length of 1
  with bottom left corner at the origin.\\
  Independence?\\
  $$
    f(x,y) = \begin{cases} 1 & (x,y) \in [0,1] \times [0,1]\\ 0 & 
      \text{otherwise}\end{cases}
  $$
  Marginal densities:\\
  $$
    f_X(x) = 1 
  $$
  if $x \in [0,1]$.\\
  $$
    f_Y(y) = 1
  $$
  if $y \in [0,1]$.\\
  This is independent.\\\\
  Let $f(x,y)$ be distributed under the curve $y = x$.
  $$
    f(x,y) = \begin{cases} 2 & 0 \le y \le x \le 1\\ 0 & \text{otherwise} 
      \end{cases}
  $$
  Marginal densitites:\\
  $$
    f_X(x) = 2x
  $$
  if $x \in [0,1]$
  $$
    f_Y(y) = 2(1-y)
  $$
  if $y \in [0,1]$\\
  They are not distributed uniformly and they're no longer independent in this
  case.\\\\
  \underline{Note}: The only way for two variables to be indepdent in a 
  continuous setting is if it distributed uniformly to a rectangle.\\\\
  \underline{Example}: Mr. and Mrs. Smith agree to meet at a place "between
  5 and 6 p.m". Assume that they both go there at a random time and are 
  indepdent.\\
  \begin{enumerate}
    \item Find the density for the time one of them will have to wait for the 
    other.
    \item Mrs. Smith later tells you she had to wait. Probability that Mr. Smith
      arrived before 5:30 given that.
  \end{enumerate}
  Let $X$ be the time when Mr. Smith arrives and
  $Y$ be the time when Mrs. Smith arrives.\\
  We will assume that $(X,Y)$ is uniform on $[0,1] \times [0,1]$.\\
  Our unit is 1 hr\\
  \underline{(Part 1)}: Let $T = |X - Y|$.\\
  Let $t \in [0,1]$ since $t$ is the difference between $x$ and $y$.
  \begin{eqnarray*}
    P(T \le t) & = & P(|X - Y| \le t)\\
      & = & P(-t \le X - Y \le t)\\
      & = & P(X - t \le Y \le X + t)\\
      & = & 1 - (1-t)^2 \text{ Take the area of the two triangles and subtract
        their area off the unit square}\\
      & = & 2t - t^2
  \end{eqnarray*}
  $$
    f_T(t) = 2 - 2t
  $$
  \underline{(Part 2)}: 
  \begin{eqnarray*}
    P( X \le .5 | X > Y ) & = & \frac{P(X \le .5, X > Y)}{P(X > Y)}\\
      & = & \frac{\frac{1}{8}}{\frac{1}{2}}\\
      & = & \frac{1}{4}\\
  \end{eqnarray*}
  \\\\
  \underline{Example}: Assume $X$ and $Y$ are independent.\\
  $X$ is uniform on $[0,1]$ and $Y$ has density, $f_Y(y) = 2y$, if 
  $y \in [0,1]$.\\
  Compute $P(X+Y \le 1)$\\
  $$
    f(x,y) = \begin{cases} 2y & (x,y) \in [0,1] \times [0,1]\\
      0 & \text{otherwise} \end{cases}
  $$
  We know that it is $2y$ because $X$ and $Y$ are independent and $P(X) = 1$
  and $P(Y) = 2y$ where $(X,Y) \in [0,1] \times [0,1]$.\\
  $$
    \int_0^1 \,dx \int_0^{1-x} 2y\,dy
  $$
  or
  $$
    \int_0^1 \,dy \int_0^{1-y} 2y\,dx
  $$
