\section*{3/9}
      \underline{Example}: Assume that an urn contains 10 black, 7 red, and 
      15 white balls. Take 5 balls out.
      \begin{enumerate}
        \item with replacement
        \item without replacement
      \end{enumerate}
      and $W$ is the number of white balls pulled out. Compute $EW$.\\\\
      $$
        EW = 5 \cdot \frac{5}{22}
      $$
      Let $Y$ be the number of different colors.\\
      Let $I_b$ be the event where black is represented.\\
      Let $I_r$ be the event where red is represented.\\
      Let $I_w$ be the event where white is represented.\\
      We know that $Y = I_b + I_r + I_w$.\\
      $$
        EY = 1 - \frac{\binom{12}{5}}{\binom{22}{5}} + 1 - 
        \frac{\binom{15}{5}}{\binom{22}{5}} + 1 - \frac{\binom{17}{5}}
        {\binom{22}{5}}
      $$
  \subsection*{More Properties of expectation}
    If $X$ and $Y$ are independent, 
    $$
      E[g(X)h(Y)] = Eg(X) \cdot E[h(Y)]
    $$
    \begin{proof}
      \begin{eqnarray*}
        E[g(X)h(Y)] & = &
        \int\int g(x)h(y)f(x,y)\,dx\,dy\\
        & = & \int\int g(x)h(y)f_X(x)g_Y(y)\,dxdy\\
        & = & \int g(x)f_X(x)\,dx \int h(y)f_Y(y)\,dy\\
        & = & Eg(X) \cdot Eh(Y)
      \end{eqnarray*}
    \end{proof}
  \noindent
  \underline{Example}: The right triangle from last time.\\
  $(X,Y)$ is a random point on the right triangle of sides of length 1.\\
  We computed that $EXY = \frac{1}{12}$ and $EX = EY = \frac{1}{3}$.\\
  Therefore, this problem is not independent $\frac{1}{3} \cdot \frac{1}{3} 
  \not= \frac{1}{12}$.\\\\
  Now, let's look at another problem. Let's say that $(X,Y)$ is a random point
  on the square of length 1.\\
  This problem in fact has $X$ and $Y$ independent because $EXY = EX \cdot 
  EY = \frac{1}{4}$.\\\\
  \underline{Example}: Roll a die and then toss as many coins as shown up
    on the die.\\
    $E(\text{number of heads})$?\\
    Assume that $(X,Y)$ is discrete. Say we know how to compute $E(Y|
    X = x)$. Now, I claim that 
    $$
      EY = \sum_x E(Y | X = x) \cdot P(X = x)
    $$
    Now, 
    \begin{eqnarray*}
      \sum_y yP(Y = y | X = x) & = & \sum_y y\frac{P(X = x | Y = y)}{P(X = x)}\\
      \sum_x E(Y|X = x) P(X = x) & = & \sum_x \sum_y y\frac{P(X = x, y = y)}
      {P(X = x)} P(X=x)\\
      & = & \sum_x \sum_y yP(X = x, y = y)\\
    \end{eqnarray*}
    In the continuous case,
    $$
      EY = \int E(Y | X = x) f_X(x) \,dx 
    $$
    \begin{eqnarray*}
      P(Y | X = x) & = & x \frac{1}{2}\\
    \end{eqnarray*}
    Let $X$ be the number on the die when $x = 1, 2, \ldots, 6$ and $Y$
    be the number of heads.
    Therefore, 
    \begin{eqnarray*}
      E(\text{number of heads}) & = & E[Y]\\
      & = & \sum_{x = 1}^6 x \frac{1}{2} \cdot \frac{1}{6}\\
      & = & \frac{7 \cdot 6}{2} \frac{1}{12}\\
      & = & \frac{7}{4}
    \end{eqnarray*}
    \underline{Example}: A person dies and presented with 3 doors. There's
      one that leads to heaven, one that leads to 1 day in purgatory, and one
      that leads to 2 days in purgatory. After staying in purgatory, you go
      back to the door and pick again.  Choose one at random each time. 
      The doors are reshuffled each time you come back.\\
      What is your expected stay in purgatory?\\
      Let $N$ be the number of days in purgatory.\\
      Conditional expectation of $N$ given you picked door $i$ where $i = 
      1,2,3$.\\
      $$
        E(N | \text{door}_1) = 0
      $$ 
      $$
        E(N | \text{door}_2) = 1 + EN
      $$
      $$
        E(N | \text{door}_i) = 2 + EN
      $$
      Therefore,
      \begin{eqnarray*}
        EN & = & \frac{1}{3}(1 + EN) + \frac{1}{3}(2 + EN)\\
        \frac{1}{3} EN & = & 1\\
        EN & = & 3
      \end{eqnarray*}
